Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-11 journal/content.tex
Comment on a very close background match
Fixed mistakes with study count numbers

@@

The results of this study include findings from 52 primary studies presenting
how 42 different large software organizations introduce agile methods. Most of
the included studies were experience reports (45 studies), and in many cases it
was evident that the author had been personally involved in the transformation.
Only 6 of the included studies had a research method explicitly stated. One of
the studies was an interview article. The publication forums of the primary
studies were distributed so that 57 sources were conference proceedings, 4
sources were journal articles, and one source was a technical report.

@@

The goal of this work was to review and analyze empirical studies of large
organizations taking agile software development methods into use. By applying
the method of systematic literature review we analyzed the findings of 52
studies describing the agile transformation in 40 different organizations. As a
result we presented qualitative findings describing typical reasons to change,
characteristics of transformations, challenges, and success factors.

>>>>

% Rohunen 2010:
% Approaches to Agile Adoption in Large Settings: A Comparison of the Results
% from a Literature Analysis and an Industrial Inventory

@@

The results of this study include findings from 52 primary studies presenting
how 42 different large software organizations introduce agile methods. Most of
the included studies were experience reports (45 studies), and in many cases it
was evident that the author had been personally involved in the transformation.
Only 6 of the included studies had a research method explicitly stated. One of
the studies was an interview article. The publication forums of the primary
studies were distributed so that 47 sources were conference proceedings, 4
sources were journal articles, and one source was a technical report.

@@

The goal of this work was to review and analyze empirical studies of large
organizations taking agile software development methods into use. By applying
the method of systematic literature review we analyzed the findings of 52
studies describing the agile transformation in 42 different organizations. As a
result we presented qualitative findings describing typical reasons to change,
characteristics of transformations, challenges, and success factors.
